The Lipid Interactome Repository

### 2025-08-06 HourlyTracking/202507_GG-Hours.qmd
Updated legends on the RM_2021 page

---
title: "July 2025 Lipid Interactome Monthly Invoice"
author: "Gaelen Guzman"
date: "2025 08 04"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 08 04}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

>>>>

---
titlJuly 2025 Lipid Interactome Monthly Invoice"
author: "Gaelen Guzman"
date: "2025 08 04"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
  - "\\fancyhead[R]{2025 08 04}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

### 2025-08-06 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
Updated legends on the RM_2021 page

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

>>>>

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). Original publication reported results in terms of peptide spectral matches; here, data have been reanalyzed to compare normalized intensities of experimental (+UV)and control (-UV) samples without isobaric mass tags. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. Original publication reported results in terms of peptide spectral matches; here, data have been reanalyzed to compare normalized intensities of experimental (+UV)and control (-UV) samples without isobaric mass tags. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis). Original publication reported results in terms of peptide spectral matches; here, data have been reanalyzed to compare normalized intensities of experimental (+UV)and control (-UV) samples without isobaric mass tags. Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

### 2025-08-06 StudyInformation_includes/RM_2021_include.qmd
adding a draft of the NAPE page
Updated legends on the RM_2021 page

[PI(3,4,5)P~3~](/LipidProbe/PhosphatidylinositolTrisphosphate.qmd)

@@

Peptide spectral counting

@@

>>>>

[Trifunctional PI(3,4,5)P~3~](/LipidProbe/PhosphatidylinositolTrisphosphate.qmd)

@@

Peptide spectral counting *(in original publication)*

Label free quantification *(as reported here, enabled via fresh analysis by Frank Stein, EMBL)*

@@

Samples were split into membrane and cytosolic fractions and analyzed as independent mass spec samples. Additional *No Probe* controls were included for raw input, though not used in displaying the data on this site.
